A distance metric between histograms derived from the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses

### 2015-11-04 tables/tabNormNull.tex
adicionadas tabelas com mudanca de amostragem

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 9 & 3 & 4 \\\hline
5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 3 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for significance levels $\alpha$.
The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8137$ and $\sigma(c_1)=0.2619$,
 $\mu(c_2)=0.7806$ and $\sigma(c_2)=0.2453$,
 $\mu(c_3)=0.8157$ and $\sigma(c_3)=0.2413$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 12 & 3 & 11 \\\hline
5.0 & 0.050 & 1.36 & 7 & 0 & 8 \\\hline
2.5 & 0.025 & 1.48 & 1 & 0 & 4 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 1 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
        of the null hypothesis for significance levels $\alpha$.
        The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
        The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
        The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
        Over all $N_c$ comparisons,
         $\mu(c_1)=0.8461$ and $\sigma(c_1)=0.2750$,
         $\mu(c_2)=0.7788$ and $\sigma(c_2)=0.2203$,
         $\mu(c_3)=0.8660$ and $\sigma(c_3)=0.2820$ .
        }
\end{center}
\end{table}

### 2015-11-04 tables/tabNormNull_.tex
adicionadas tabelas com mudanca de amostragem

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 9 & 3 & 4 \\\hline
5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 3 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for significance levels $\alpha$.
The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8137$ and $\sigma(c_1)=0.2619$,
 $\mu(c_2)=0.7806$ and $\sigma(c_2)=0.2453$,
 $\mu(c_3)=0.8157$ and $\sigma(c_3)=0.2413$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 12 & 3 & 11 \\\hline
5.0 & 0.050 & 1.36 & 7 & 0 & 8 \\\hline
2.5 & 0.025 & 1.48 & 1 & 0 & 4 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 1 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
        of the null hypothesis for significance levels $\alpha$.
        The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
        The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
        The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
        Over all $N_c$ comparisons,
         $\mu(c_1)=0.8461$ and $\sigma(c_1)=0.2750$,
         $\mu(c_2)=0.7788$ and $\sigma(c_2)=0.2203$,
         $\mu(c_3)=0.8660$ and $\sigma(c_3)=0.2820$ .
        }
\end{center}
\end{table}

### 2015-11-04 tables/tabPowerNull.tex
adicionadas tabelas com mudanca de amostragem

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 6 & 8 & 7 & 6 & 7 \\\hline
5.0 & 0.050 & 1.36 & 3 & 5 & 4 & 2 & 5 \\\hline
2.5 & 0.025 & 1.48 & 2 & 0 & 2 & 2 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 2 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8171$ and $\sigma(c_1)=0.2314$,
 $\mu(c_2)=0.8486$ and $\sigma(c_2)=0.2519$,
 $\mu(c_3)=0.8135$ and $\sigma(c_3)=0.2607$ .
 $\mu(c_4)=0.8238$ and $\sigma(c_4)=0.2360$ .
 $\mu(c_5)=0.8343$ and $\sigma(c_5)=0.2426$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 3 & 6 & 8 & 9 & 9 \\\hline
5.0 & 0.050 & 1.36 & 1 & 4 & 4 & 4 & 4 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 2 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 0 & 2 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 1 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
        of the null hypothesis for critical values of $\alpha$.
        The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
        The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
        The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
        The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
        The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
        Over all $N_c$ comparisons,
         $\mu(c_1)=0.7569$ and $\sigma(c_1)=0.2238$,
         $\mu(c_2)=0.8068$ and $\sigma(c_2)=0.2551$,
         $\mu(c_3)=0.8591$ and $\sigma(c_3)=0.2466$ .
         $\mu(c_4)=0.8481$ and $\sigma(c_4)=0.2514$ .
         $\mu(c_5)=0.8314$ and $\sigma(c_5)=0.2768$ .
        }
\end{center}
\end{table}

### 2015-11-04 tables/tabPowerNull_.tex
adicionadas tabelas com mudanca de amostragem

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 6 & 8 & 7 & 6 & 7 \\\hline
5.0 & 0.050 & 1.36 & 3 & 5 & 4 & 2 & 5 \\\hline
2.5 & 0.025 & 1.48 & 2 & 0 & 2 & 2 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 2 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8171$ and $\sigma(c_1)=0.2314$,
 $\mu(c_2)=0.8486$ and $\sigma(c_2)=0.2519$,
 $\mu(c_3)=0.8135$ and $\sigma(c_3)=0.2607$ .
 $\mu(c_4)=0.8238$ and $\sigma(c_4)=0.2360$ .
 $\mu(c_5)=0.8343$ and $\sigma(c_5)=0.2426$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 3 & 6 & 8 & 9 & 9 \\\hline
5.0 & 0.050 & 1.36 & 1 & 4 & 4 & 4 & 4 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 2 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 0 & 2 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 1 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
        of the null hypothesis for critical values of $\alpha$.
        The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
        The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
        The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
        The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
        The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
        Over all $N_c$ comparisons,
         $\mu(c_1)=0.7569$ and $\sigma(c_1)=0.2238$,
         $\mu(c_2)=0.8068$ and $\sigma(c_2)=0.2551$,
         $\mu(c_3)=0.8591$ and $\sigma(c_3)=0.2466$ .
         $\mu(c_4)=0.8481$ and $\sigma(c_4)=0.2514$ .
         $\mu(c_5)=0.8314$ and $\sigma(c_5)=0.2768$ .
        }
\end{center}
\end{table}

### 2015-11-04 tables/tabUniformNull.tex
adicionadas tabelas com mudanca de amostragem

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
 $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
 $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 8 & 9 & 14 \\\hline
5.0 & 0.050 & 1.36 & 2 & 3 & 8 \\\hline
2.5 & 0.025 & 1.48 & 1 & 3 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 1 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
        of the null hypothesis for critical values of $\alpha$.
        The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
        The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
        The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
        Over all $N_c$ comparisons,
         $\mu(c_1)=0.8215$ and $\sigma(c_1)=0.2468$,
         $\mu(c_2)=0.7938$ and $\sigma(c_2)=0.2874$,
         $\mu(c_3)=0.8611$ and $\sigma(c_3)=0.2831$ .
        }
\end{center}
\end{table}

### 2015-11-04 tables/tabUniformNull_.tex
adicionadas tabelas com mudanca de amostragem

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 9 & 8 & 8 \\\hline
5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
2.5 & 0.025 & 1.48 & 1 & 2 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 2 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8616$ and $\sigma(c_1)=0.2291$,
 $\mu(c_2)=0.8345$ and $\sigma(c_2)=0.2492$,
 $\mu(c_3)=0.8086$ and $\sigma(c_3)=0.2740$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 8 & 9 & 14 \\\hline
5.0 & 0.050 & 1.36 & 2 & 3 & 8 \\\hline
2.5 & 0.025 & 1.48 & 1 & 3 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 1 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
        of the null hypothesis for critical values of $\alpha$.
        The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
        The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
        The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
        Over all $N_c$ comparisons,
         $\mu(c_1)=0.8215$ and $\sigma(c_1)=0.2468$,
         $\mu(c_2)=0.7938$ and $\sigma(c_2)=0.2874$,
         $\mu(c_3)=0.8611$ and $\sigma(c_3)=0.2831$ .
        }
\end{center}
\end{table}

### 2015-11-04 tables/tabWeibullNull.tex
adicionadas tabelas com mudanca de amostragem

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 5 & 8 & 7 \\\hline
5.0 & 0.050 & 1.36 & 0 & 3 & 6 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 1 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.1154$ and $\sigma(c_1)=0.0759$,
 $\mu(c_2)=0.8057$ and $\sigma(c_2)=0.2556$,
 $\mu(c_3)=0.8531$ and $\sigma(c_3)=0.2638$ .
 $\mu(c_4)=0.8240$ and $\sigma(c_4)=0.2414$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 5 & 7 & 8 \\\hline
5.0 & 0.050 & 1.36 & 0 & 3 & 5 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 2 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
        of the null hypothesis for critical values of $\alpha$.
        The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
        The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
        The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
        Over all $N_c$ comparisons,
        The $N_o$ values of $c_4$ were calculated using simulations of
         1-parameter Weibull distributions with $a=6$.
        Over all $N_c$ comparisons,
         $\mu(c_1)=0.1089$ and $\sigma(c_1)=0.0642$,
         $\mu(c_2)=0.8186$ and $\sigma(c_2)=0.2124$,
         $\mu(c_3)=0.7905$ and $\sigma(c_3)=0.2701$ .
         $\mu(c_4)=0.8063$ and $\sigma(c_4)=0.2437$ .
        }
\end{center}
\end{table}

### 2015-11-04 tables/tabWeibullNull_.tex
adicionadas tabelas com mudanca de amostragem

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 0 & 5 & 8 & 7 \\\hline
5.0 & 0.050 & 1.36 & 0 & 3 & 6 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 1 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.1154$ and $\sigma(c_1)=0.0759$,
 $\mu(c_2)=0.8057$ and $\sigma(c_2)=0.2556$,
 $\mu(c_3)=0.8531$ and $\sigma(c_3)=0.2638$ .
 $\mu(c_4)=0.8240$ and $\sigma(c_4)=0.2414$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 0 & 5 & 7 & 8 \\\hline
5.0 & 0.050 & 1.36 & 0 & 3 & 5 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 2 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
        of the null hypothesis for critical values of $\alpha$.
        The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
        The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
        The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
        Over all $N_c$ comparisons,
        The $N_o$ values of $c_4$ were calculated using simulations of
         1-parameter Weibull distributions with $a=6$.
        Over all $N_c$ comparisons,
         $\mu(c_1)=0.1089$ and $\sigma(c_1)=0.0642$,
         $\mu(c_2)=0.8186$ and $\sigma(c_2)=0.2124$,
         $\mu(c_3)=0.7905$ and $\sigma(c_3)=0.2701$ .
         $\mu(c_4)=0.8063$ and $\sigma(c_4)=0.2437$ .
        }
\end{center}
\end{table}
